Analyzing Fairness: Race, Recidivism, and the COMPAS Algorithm

### 2022-04-21 final_metrics_analysis.Rmd
adding citations

# for Dianne
use_condaenv("base")

@@

If a defendant has a higher number of prior offenses, the individual is more likely to be rated with a higher risk of recidivism **do we know this for sure?**. In the former plot, we can see that Black defendants have a higher number of prior charges than do white defendants. This again likely reflects the over-policing of Black people and communities. In the latter plot, we can see that male defendants have a higher number of prior charges than do female defendants. This is worth noting because the COMPAS risk assessment algorithm has been found to express a discrepancy in prediction between sexes **who found this?**. When the recidivsim predictions are compared with the true recividism outcomes, female defendants have a notable false positive rate that predicts their recidivism risk as higher than their true outcomes**where does this come from?**.

>>>>

# for Dianne
#use_condaenv("base")

@@

In the former plot, we can see that Black defendants have a higher number of prior charges than do white defendants. This again likely reflects the over-policing of Black people and communities. In the latter plot, we can see that male defendants have a higher number of prior charges than do female defendants. This is worth noting as @larson2016we found that there is discrepancy in COMPAS risk assessment algorithm's prediction between sexes. When the recidivsim predictions are compared with the true recividism outcomes, female defendants have a notable false positive rate that predicts their recidivism risk as higher than their true outcomes [@larson2016we].
